\documentclass[12pt,english,oneside]{scrbook}
\usepackage{ae,aecompl}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
%\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0pt}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{setspace}
\setstretch{1.1}

\makeatletter
\numberwithin{equation}{chapter}
\theoremstyle{definition}
\newtheorem*{example*}{\protect\examplename}
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}[section]

\@ifundefined{date}{}{\date{}}
\AtBeginDocument{
\addtolength{\abovedisplayskip}{0ex}
\addtolength{\abovedisplayshortskip}{0ex}
\addtolength{\belowdisplayskip}{0ex}
\addtolength{\belowdisplayshortskip}{0ex}
}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem*{corollary*}{Corollary}

\makeatother

\usepackage{babel}
\providecommand{\examplename}{Example}
\providecommand{\theoremname}{Theorem}

\begin{document}


\title{Economics: Cheatsheet}
\author{Ronald Mangang}

\maketitle
\tableofcontents

\thispagestyle{empty}
\newpage
\pagenumbering{arabic}

\part{Microeconomics}

\chapter{Market Equilibrium}

\paragraph{Demand function.}

\paragraph{Demand curve.}

\paragraph{Shift in demand curve.}

\paragraph{Individual demand vs market demand.}

\paragraph{Normal good vs inferior good.}

\paragraph{Supply function.}

\paragraph{Supply curve.}

\paragraph{Market equilibrium.}

\paragraph{Price elasticity.}

\paragraph{Elasticity and revenue.}




\chapter{Consumer Behavior}

\paragraph{Indifference curve.}

Marginal Rate of Substitution (M.R.S.) = slope

\paragraph{Budget line.}

Marginal utility = $\displaystyle\frac{\partial u}{\partial x}$.

\paragraph{Consumer equilibrium.}

Indifference curve intersects the budget line.

M.R.S. = $\displaystyle\frac{p_1}{p_2}$ = slope of the budget line.

\paragraph{Equal marginal principle.}

Deduce the conditions of consumer equilibrium using Langragian multipliers.

\chapter{Producer Behavior}

\paragraph{Production function.}

Output, $Q = f(L, k, \text{land}, \text{efficiency}, \ldots)$.

Marginal productivities:
\begin{itemize}
\item M.P.$_L$ = $\displaystyle \frac{dQ}{dL}$
\item M.P.$_k$ = $\displaystyle \frac{dQ}{dk}$
\end{itemize}

\paragraph{Isoquant curve.}

A curve that displays combinations of labor $L$ and capital $k$ for the same output.

Marginal Rate of Technical Substitution (M.R.T.S.) = slope.

\paragraph{Returns to scale.}

Can be increasing, constant or decreasing.

\paragraph{Costs.}

Total cost (T.C.) = fixed cost (F.C.) + variable cost (V.C.)

Marginal cost (M.C.) = $\displaystyle \frac{d(T.C.)}{dQ} = \frac{d(V.C.)}{dQ}$.

V.C. = $rk + wL$, where $r$ is the rate of interest and $w$ is the wage.

Suppose $k$ is held constant. We obtain
\[
  M.C. = \frac{w}{M.P._L}
\]

Repeat the same by holding $L$ constant.

\paragraph{Iso-cost line.}

$rk + wL = $ const.

slope = $\displaystyle \frac{w}{r}$.

\paragraph{Optimizing production subject to fixed cost.}

$\displaystyle \frac{M.P._L}{M.P._k} = \frac{w}{r}$.

\paragraph{Optimizing cost subject to fixed production.}




\end{document}


